---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# thaigov

<!-- badges: start -->
[![R-CMD-check](https://github.com/asiripanich/thaigov/workflows/R-CMD-check/badge.svg)](https://github.com/asiripanich/thaigov/actions)
<!-- badges: end -->

The goal of thaigov is to provide an easy access to the datasets on the [Open Government Data of Thailand](https://data.go.th/) API from R.

The Thai documentation of the API can be viewed here: https://opendata.data.go.th/pages/data-go-th-api.

## Installation

You can install the development version of thaigov from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("asiripanich/thaigov")
```

## Example

First put your Open Government Data of Thailand API key in your machine's `.Renviron` file. 
I normally use `usethis::edit_r_environ()` to find and open my `.Renviron` file.
Insert the your API key in the following format: `THGOV_OPENDATA_TOKEN=<your-API-key>`.

```{r example}
library(thaigov)
library(tibble)

covid_resources <- th_resource_search("โควิด") # search for resources that contain the word "COVID" in Thai in their description.
covid_resources %>% as_tibble()
covid_csv_datasets <- covid_resources %>%
  .[format == "CSV" & !is.na(resource_id), resource_id] %>%
  lapply(function(x) th_get(x) %>% as_tibble())
covid_csv_datasets

th_package_list() %>% sample(size = 10)
# th_package_search("โควิด") # search for packages that contain the word "COVID" in Thai.
# ​th_package_show("3e9d9124-d187-4fc7-b2fb-22c681ceb4fe")
```
